\cvsection{Experience}

\begin{cventries}
  \cventry
    {Full Stack Engineer} % Job title
    {Blend-ed} % Organization
    {Calicut, Kerala (Remote)   } % Location
    {Apr. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Internship}
        \item Open edX development with Tutor
        \item Implemented SSO login integration with Auth0 JWT for secure user access.
        \item Designed and implemented a custom Django OAuth plugin for seamless Auth0 integration.
        \item Integrated Hasura GraphQL backend with React frontend for efficient data management.
        \item Migrated SMS functionalities from Twilio to AWS SNS using AWS Lambda, enhancing scalability and cost-effectiveness.
        \vspace{2mm}
        \item \textbf{Full time Flexible}
        \item Tutor k8s implementation
        \item Maintained Docker images for deployment in AWS ECR, ensuring efficient container management.
        \item Developed custom GCP cloud functions to handle login, program enrollment, and Open edX-Frontend data synchronization.
        \item Implemented Tutor Cairn analytics for data-driven decision-making and integrated it with Superset Cairn Embed for visual insights.
        \item Implemented instructor/student chat
      \end{cvitems}
    }

  \cventry
    {Content Research and Web Development Intern} % Job title
    {HighQ} % Organization
    {Remote} % Location
    {Jul. 2021 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Automated content synchronization from Excel sheets to WordPress website, improving efficiency and accuracy.
        \item Conducted comprehensive research on state-level universities and their eligibility criteria, contributing to data-driven decision-making.
      \end{cvitems}
    }
    
\end{cventries}
